Analytical choices for analyzing multidimensional behavior - many analyst test hypotheses about human speech.

### 2020-10-19 RR_manuscript/Draft_RR.tex
Light edits, fixed some typos, put each sentence on its own line, added bib file for refs

In order to effectively accumulate knowledge, science needs to (i) produce data that can be recreated by using the same methods and (ii) arrive at conclusions about data that are robust. In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low succes rates for (i) (e.g., Open Science Collaboration 2015, Camerer et al.~2018, REF) leading to what is now referred to as the \emph{replication crisis}. Beyond difficulties replicating scientific findings, more and more evidence suggests that the theoretical conclusions drawn from data are surprisingly variable even if researchers have access to reliable data (REFS). The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit \& Dubé 2015, Starns et al.~2019) and is, among other things, rooted in the inherent flexibility of data analysis, often referred to as researcher degrees of freedom (Simmons, Nelson, \& Simonsohn, 2011, Gelman \& Loken 2013). Data analysis involves many different steps including inspecting, organizing, transforming, and modeling the data. Along the way, different methodological and analytical choices need to be made, all of which might change its final interpretation. These researcher degrees of freedom are a blessing and a curse at the same time.

There are a blessing, because they allow us to look at nature from many different angles allowing us to make important discoveries and generate new hypothesis (e.g.~Box 1976, Tukey 1977, de Groot 2014). They are a curse because idiosyncratic choices can lead to categorically different interpretation which find their way into the publication record where they are taken for granted (Simmons et al.~2011). Recent projects have shown that the variability between different data analysts is immense and leads researchers to draw vastly different conclusions about one and the same dataset (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020). These projects, however, might still underestimate the extend to which analysts vary because data analysis is not only restricted to statistical inference of data tables. Human behavior is complex and offers many ways to be translated into numbers. This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like speech or video data. In fields working on human speech production for example, researchers need to make many decisions about what to measure and how to measure it. This is not trivial given the temporal extension of the acoustic signal and its complex structural composition. Decisions about operationalizing the raw data might not only influence downstream decisions about statistical modelling but statistical results might lead researchers to go back and revise earlier decisions about the raw data.

In this article, we investigate the diversity in analytic choices when many analyst teams analyze the same speech production data. We explore the interaction between analytic choices at the stage of the operationalization of raw data and subsequent statistical modelling. Specifically we report the impact of analytic pipeline on research results obtained by \#\# teams that gained access to the same raw data set to answer the same research question.

@@

Data analysis comes with many decisions like how to operationalize a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude, what models to use or what inferential decision procedure to apply.However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes. This can be problematic because to err is human.

@@

In a collaborative effort, Silberzahn et al.~(2018) let twenty-nine independent analysis teams address the same research question. Analytic approaches and consequently the results varied widely between teams. 69\% of the teams found support for the hypothesis, and 31\% did not. Out of the 29 analysis strategies, there were 21 unique combinations of covariates. Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
Their results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias. Similar crowd-sourced studies recruiting independent analyst teams showed similar results.

Neuroscience
Cognitive Modelling
Clinical
Predictive models

@@

\emph{(copy pasted from RDF paper and slightly shortened by myself. I think its a good point of departure. Maybe one of your can try to rephrase it in your own words?)}
RELEVANCE OF SPEECH PRODUCTION RESEARCH FOR COGSCI, AI, etc.

@@

This account, however, has mainly focused on content selection (Gatt et al.~2013), i.e.~whether a certain referential expression is chosen or not. However, speech communication is so much richer. Even looking at morphosyntactically identical expressions, speakers can modulate this expression via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g.~Ladd 2008). Most prominently, languages use intonation to signal discourse relationships between referents (among other functions). Intonation marks discourse-relevant referents for being new or given information to guide listeners' interpretation of incoming messages. In many languages, speakers can use particular pitch movements to signal whether a referent has already been mentioned and is therefore referred back to, or a referent is newly introduced into the discourse. Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse. Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on \enquote{banana} to indicate the contrastive nature of the \emph{noun.} In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on \enquote{yellow} to indicate the contrastive nature of the \emph{modifier.} In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.~segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.

INFORMATION ABOUT THE DATA SET

@@

We used R (Version 4.0.2; R Core Team, 2020) and the R-package \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020) for all our analyses.

@@

>>>>

In order to effectively accumulate knowledge, science needs to (i) produce data that can be recreated by using the same methods and (ii) arrive at conclusions about data that are robust.
In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low succes rates for (i) (e.g., Open Science Collaboration, 2015; Camerer et al., 2018) leading to what is now referred to as the \emph{replication crisis}.
Beyond difficulties replicating scientific findings, more and more evidence suggests that the theoretical conclusions drawn from data are surprisingly variable even if researchers have access to reliable data (REFS).
The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit \& Dubé 2015, Starns et al.~2019) and is, among other things, rooted in the inherent flexibility of data analysis, often referred to as researcher degrees of freedom (Simmons, Nelson, \& Simonsohn, 2011, Gelman \& Loken 2013).
Data analysis involves many different steps including inspecting, organizing, transforming, and modeling the data.
Along the way, different methodological and analytical choices need to be made, all of which might change its final interpretation.
These researcher degrees of freedom are a blessing and a curse at the same time.

There are a blessing, because they allow us to look at nature from many different angles allowing us to make important discoveries and generate new hypothesis (e.g.~Box 1976, Tukey 1977, de Groot 2014).
They are a curse because idiosyncratic choices can lead to categorically different interpretation which find their way into the publication record where they are taken for granted (Simmons et al.~2011).
Recent projects have shown that the variability between different data analysts is immense and leads researchers to draw vastly different conclusions about one and the same dataset (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
These projects, however, might still underestimate the extent to which analysts vary because data analysis is not only restricted to statistical inference of data tables.
Human behavior is complex and offers many ways to be translated into numbers.
This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like speech or video data.
In fields working on human speech production for example, researchers need to make many decisions about what to measure and how to measure it.
This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
Decisions about operationalizing the raw data might not only influence downstream decisions about statistical modelling but statistical results might lead researchers to go back and revise earlier decisions about the raw data.

In this article, we investigate the diversity in analytic choices when many analyst teams analyze the same speech production data.
We explore the interaction between analytic choices at the stage of the operationalization of raw data and subsequent statistical modelling.
Specifically we report the impact of analytic pipeline on research results obtained by XX teams that gained access to the same raw data set to answer the same research question.

@@

Data analysis comes with many decisions like how to operationalize a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude, what models to use or what inferential decision procedure to apply.
However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
This can be problematic because to err is human.

@@

In a collaborative effort, Silberzahn et al.~(2018) let twenty-nine independent analysis teams address the same research question.
Analytic approaches and consequently the results varied widely between teams.
Sixty-nine percent of the teams found support for the hypothesis, and 31\% did not.
Out of the 29 analysis strategies, there were 21 unique combinations of covariates.
Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
Their results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias.
Similar crowd-sourced studies recruiting independent analyst teams showed similar results.

Neuroscience\\
Cognitive Modelling\\
Clinical\\
Predictive models

@@

\emph{(copy pasted from RDF paper and slightly shortened by myself. I think its a good point of departure. Maybe one of your can try to rephrase it in your own words?)}

RELEVANCE OF SPEECH PRODUCTION RESEARCH FOR COGSCI, AI, etc.

@@

This account, however, has mainly focused on content selection (Gatt et al.~2013), i.e.~whether a certain referential expression is chosen or not.
However, speech communication is so much richer.
Even looking at morphosyntactically identical expressions, speakers can modulate this expression via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g.~Ladd 2008).
Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
Intonation marks discourse-relevant referents for being new or given information to guide listeners' interpretation of incoming messages.
In many languages, speakers can use particular pitch movements to signal whether a referent has already been mentioned and is therefore referred back to, or a referent is newly introduced into the discourse.
Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse.
Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on \enquote{banana} to indicate the contrastive nature of the \emph{noun}.
In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on \enquote{yellow} to indicate the contrastive nature of the \emph{modifier}. In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.~segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.

INFORMATION ABOUT THE DATA SET AND EXP DESIGN

@@

We used R (Version 4.0.3; R Core Team, 2020) and the R-package \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020) for all our analyses.

@@

\leavevmode\hypertarget{ref-camerer2018evaluating}{}%
Camerer, C. F., Dreber, A., Holzmeister, F., Ho, T.-H., Huber, J., Johannesson, M., \ldots{} others. (2018). Evaluating the replicability of social science experiments in nature and science between 2010 and 2015. \emph{Nature Human Behaviour}, \emph{2}(9), 637--644. \url{https://doi.org/10.1038/s41562-018-0399-z}

\leavevmode\hypertarget{ref-open2015estimating}{}%
Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251). \url{https://doi.org/10.1126/science.aac4716}
